### 2014-03-13 Draft/introduction.tex
Updated the project Web

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item An NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
	\item An evaluation of proposed approach on 
commonly used package \CodeIn{java.io} from JDK API and Amazon
S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
an average of 70\% precision and 80\% recall in inferring 63
temporal constraints from more than 2400 sentences of API
documents.
\end{itemize}

>>>>

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item An NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
	\item An evaluation of proposed approach on commonly used package \CodeIn{java.io} from JDK API and \amazonAPI. 
\end{itemize}
